Many Analystis Project

### 2022-02-27 analysis-religious-only.Rmd
updated analysis

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
library("tidyverse")
library("easystats")
library("ggplot2") #plots
#library("sjstats") #test statistics
#library("sjPlot")
#library("sjmisc")
##library("insight")
#library("see")
#library("performance")
library("ggraph")
#library("parameters")
library("lme4")
#library("psych") ## correlation matrix
library("table1")
library("ggeffects")
#library("gghighlight")
#library("texreg")
library("kableExtra")
#library("naniar") # missingness
library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
=library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
library("WeightIt")# inverse probability weighting. 
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
```

@@

df <- d %>%
  dplyr::mutate(male2 = ifelse(gender != "man", 1 , 2)) %>% # for index categorical variable, not change of meaning for gender. male and people who do not identify as male.
  dplyr::mutate(male = factor(ifelse(gender != "man", "male" , "notmale"))) %>%
  rename(
    rel_CHURCHFREQ   = rel_1,
    # factor need to recode (eg 7 as 0)// yikes factor transformed into a number
    rel_PRAYERFREQ = rel_2,
    # factor need to recode (eg. 7 as 0)// yikes factor transformed into a number
    IS_RELIIGOUS = rel_3,
    # factor 1 = yes, 2 = no, 3 = atheist// yikes factor transformed into a number
    BELONGS_DENOMINATION = rel_4,
    # relig
    rel_EXTENTBELIEVEGOD = rel_5,
    # do you belong to a religion or religious denomination? 1 = yes, 2 = no (!)
    rel_EXTENTBELIEVEAFTERLIFE = rel_6,
    rel_EXTENTSPIRITUAL  = rel_7,
    rel_IMPORTANCERELIGIOUSLIFE = rel_8,
    # 1 to five
    rel_IMPORTANCEBELIEVEGOD = rel_9,
    # 1 to five
    wb_genLIFEQUALITY = wb_gen_1,
    # not defined # also remove second underscore, which BRMS doesn't like
    wb_genSATHEALTH = wb_gen_2,
    # not defined
    wb_phyPAIN = wb_phys_1,
    wb_physNEEDSMEDICALTREAT =  wb_phys_2,
    wb_physHASENERGY =  wb_phys_3,
    wb_physMOBILITY = wb_phys_4,
    wb_physSLEEP = wb_phys_5,
    wb_physCANDODAILYACTIVITIES  = wb_phys_6,
    wb_physSATCAPACITYWORK  = wb_phys_7,
    wb_psychENJOYLIFE = wb_psych_1,
    wb_psychMEANING  = wb_psych_2,
    wb_psychCONCENTRATE  = wb_psych_3,
    wb_psychLIKESAPPEARANCE  = wb_psych_4,
    wb_psychSATSELF  = wb_psych_5,
    wb_psychANXIETY  = wb_psych_6,
    wb_socSATPERSONALRELATIONSHIPS  = wb_soc_1,
    wb_socSATSUPPORTFRIENDS  = wb_soc_2
    #   wb_socSATSEX   = wb_soc_3,
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = as.factor(IS_RELIIGOUS),
    denomination = as.factor(denomination),
    ethnicity = as.factor(ethnicity),
    country = as.factor(country)
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = recode_factor(
      IS_RELIIGOUS,
      "0" = "atheist",
      "0.5" = "not_religious",
      "1" = "religious"
    )
  )

@@

d1 <- df %>%
  dplyr::filter(
   #  !is.na(wb_psychANXIETY),
   #  !is.na(age),
   #  !is.na(rel_CHURCHFREQ),
   # # !is.na(wb_psychMEANING),
   #  !is.na(male),
   #  !is.na(rel_EXTENTBELIEVEGOD),
  ) %>%
  dplyr::mutate(
    anx = as.integer(6- wb_psychANXIETY), # reverse coded! rescale 1-5
    #anx_s = scale(anx),
    #put outcome in ST units (see McElreath 2021)  # not necessary
    #age_s = scale(age),
    ch = rel_CHURCHFREQ,
  #  mn  = wb_psychMEANING,
    edu = education,
    bg =  rel_EXTENTBELIEVEGOD#,
  #  ch_s = scale(rel_CHURCHFREQ),
  #  mn_s = scale(wb_psychMEANING),
   # bg_s = scale(rel_EXTENTBELIEVEGOD)
  ) %>%
  dplyr::select(anx,
                ch,
                age,
                ses,
                #    mn,
                edu,
                bg,
                # anx_s,
                # age_s,
                #  ch_s,
                #  mn_s,
                edu,
                country,
                male,
                #   bg_s,
                wb_psychANXIETY)

@@

# 
# ggdag::ggdag(dg2) + theme_dag()
# 
# nocause <- ggdag::ggdag(dg2, text = FALSE, use_labels = "label")  + theme_dag() + labs(title = "Assume unmeasured distressing experience does not affect Belief or Service")
# nocause
# 
# dg0<-ggdag::ggdag_adjustment_set(dg2, node_size = 14, text = FALSE, use_labels = "label") +
#   theme(legend.position = "bottom") +
#   theme_dag() + ggtitle("Adjustment set for religious service
# assuming service does not change from distress")
# 
# dp0
# 
# 
# dpz <- dagify(
#   anx  ~ belief + church + male + country + U,
#   belief ~ age + male + country + church,
#   church ~ age + male + country,
#   ses ~ country + age + edu,
#   edu ~ country + male, 
#   U ~ age + ses + country,
#   exposure =  "belief",
#   outcome =   "anx",
#   latent = "U",
#   labels = c(
#     "belief" = "belief God",
#     "church" = "religious service attendance",
#     "anx" = "anxiety",
#     "edu" = "education",
#     "ses" = "SES",
#     "male" = "male",
#     "country" = "country",
#     "age" = "age",
#     "U" = "Unmeasured
#     distressing life events"
#   )
# )
# 
# ggdag::ggdag(dpz) + theme_dag()
# 
# 
# # graph adjustment sets
# dg1<-ggdag::ggdag_adjustment_set(dpz, node_size = 14, text = FALSE, use_labels = "label") +
#   theme(legend.position = "bottom") +
#   theme_dag() + ggtitle("Adjustment set for religious belief
# assuming belief does not change from distress")
# 
# dg1
```

@@

```{r cache = TRUE}
library("naniar")
vis_miss(df) # substantial pattern of missingness in a few variables, 
df
df$wb_soc_3
dff<-df%>%
  select(-wb_soc_3)
sum(is.na(df$education))

miss_graph<- gg_miss_upset(dff)
miss_graph
# save graph
ggsave(
  dg1,
  path = here::here("Figs"),
  width = 10,
  height = 5,
  units = "in",
  filename = "dag_church.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

@@

  # x is the longitudional dataframe (here 'd_3')
set.seed(1234)
prep <- d1 %>% # Remove what we do not need anymore
    arrange(country) %>%
    dplyr::select(anx,
                  ch,
                  age,
                  edu,
                  bg,
                  edu,
                  country,
                  male,
                  anx, 
                  ses)
# impute missing
prep <- as.data.frame(prep) # tibble won't run in amelia
set.seed(1234)
prep2 <- Amelia::amelia(
  prep,
  #dataset to impute
  m = 10,
  # number of imputations
  cs = c("country"),
  #ts = c("years"),
  noms = c(
    "male"
  ))
  #idvars = c("country")#,
  # not imputing outcomes
 # polytime = 3
)  #https://stackoverflow.com/questions/56218702/missing-data-warning-r

out <- Amelia::transform.amelia(
  prep2,
  age_s = scale(age),
  bg_s = scale(bg),
  anx_s = scale(anx),
  age_s = scale(age),
  ch_s =scale(ch),
  edu_s = scale(edu),
  ses_s = scale(ses),
  male_2 = scale(as.numeric(male))/2) # scale by 2 sds

#saveRDS(out, here::here("mods","out"))
out <-readRDS(here::here("mods","out"))
```

@@

### gee

```{r}
##
#{ age, country, edu, male, ses }
m<-10
models<-NULL
for(i in 1:m) {
  models[[i]]  <- geeglm(
  anx_s ~ bg_s + ch_s + age_s + edu_s + male_2 + ses_s,
  data = out$imputations[[i]],  
  id = country,
  corstr = "exchangeable"
)
}

# saveRDS(models, here::here(
#   "mods","models.rds")
# )

parameters::pool_parameters(models)

pred <- ggeffects::ggemmeans(models[[1]], terms = c("bg_s[all]"))
pred

plot(pred,
     add.data=T,dot.alpha=.1, 
     facets = F)  + #scale_y_continuous(limits=c(-.5,.5)) + 
  theme_classic() + ggtitle("") # title to be suppled
```

@@

```{r}
library(mice)
d2<-mice(d1)
d3<-complete(d2)
saveRDS(d3,here::here("mods","d3"))
d3 <-readRDS(here::here("mods","d3"))
d4<-d3%>%
  select(anx, ch, bg, age, edu,male,ses,country)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country))

m<-10
modelsCH<-NULL
for(i in 1:m) {
  modelsCH[[i]]  <- geeglm(
  anx_s ~  ch_s + age_s + edu_s + male_2 + ses_s,
  data = out$imputations[[i]],  
  id = country,
  corstr = "exchangeable"
)
}

saveRDS(modelsCH, here::here(
  "mods","modelsCH.rds")
)

pred <- ggeffects::ggemmeans(modelsCH[[1]], terms = c("ch_s[all]"))
pred

plot(pred,
    # add.data=T,dot.alpha=.1, 
     facets = F)  + scale_y_continuous(limits=c(-.5,.5)) + theme_classic() + ggtitle("") # title to be suppled
parameters::pool_parameters(modelsCH)

parameters::pool_parameters(modelsCH)
#parameters::pool_parameters(modelschG)

@@

dbl <- ipw::ipwpoint(
  exposure = bg_g,
  family = "gaussian",
  numerator = ~ 1,
  denominator = ~ age_s +ch_s + edu_s + male_2 + ses_s + country,
  trunc = 0.01,
  data = as.data.frame(d4)
)

@@

d1p <- d4 %>% 
  mutate(ipwCH = dch$weights.trunc,
         ipwBG = dbl$weights.trunc)

max(d1p$ipwBG)
max(d1p$ipwCH)
```

```{r}

ipb_bg<- geeglm(
  anx_s ~ bg_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable",
  weights = ipwBG
)

ipb_ch<- geeglm(
  anx_s ~  ch_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)

model_parameters(ipb_bg)

model_parameters(ipb_ch)

library(EValue)

# sensitivity = Church
evalues.OLS(-0.08, se = 0.01, sd = 1, delta = 1)

# sensitivity
evalues.OLS(0.04, se = 0.01, sd = 1, delta = 1)

@@

@@

```{r}

ipb_bg_noweights <- geeglm(
  anx_s ~ bg_s + ch_s + age_s + edu_s + male_2 + ses_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable"
)

ipb_ch_noweights <- geeglm(
  anx_s ~ ch_s + age_s + edu_s + male_2 + ses_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable"
)

model_parameters(ipb_bg_noweights)
model_parameters(ipb_bg)

model_parameters(ipb_ch_noweights)
model_parameters(ipb_ch)
```

@@

### GlMM TMB BELIEF

```{r}
library(glmmTMB)
m<-10
modelsb<-NULL
for(i in 1:m) {
  modelsb[[i]]  <- glmmTMB(anx_s ~ bg_s + ch_s + age_s + edu_s + male_2 + ses_s + 
                            (1+ bg_s|country), 
                              data = out$imputations[[i]],
                              family =)
}

parameters::pool_parameters(modelsb)

pred <- ggeffects::ggemmeans(modelsb[[1]], terms = c("bg_s[all]"))
pred

plot(pred,
    # add.data=T,dot.alpha=.1, 
     facets = F)  + scale_y_continuous(limits=c(-.2,.2)) + theme_classic() + ggtitle("") # title to be suppled
```

### GlMM TMB CHURCH

```{r}
library(glmmTMB)
m<-10
modelsC<-NULL
for(i in 1:m) {
  modelsC[[i]]  <- glmmTMB(anx_s ~  ch_s + age_s + edu_s + male_2 + ses_s + 
                            (1+ bg_s|country), 
                              data = out$imputations[[i]],
                              family =)
}

parameters::pool_parameters(modelsC)

pred <- ggeffects::ggemmeans(modelsC[[1]], terms = c("ch_s[all]"))
pred

plot(pred,
     add.data=T,dot.alpha=.05, 
     facets = F)  + theme_classic() + ggtitle("") # title to be suppled
```

### Test implied conditional independence

```{R}
m<-10
models<-NULL
for(i in 1:m) {
  models[[i]] <- lmer(anx_s ~ 
                        bg_s + 
                        ch_s + 
                        age_s + 
                        edu_s + 
                        male_2 + 
                        ses_s + 
                        (1+ bg_s|country ), data=out$imputations[[i]])
}

parameters::pool_parameters(models,
                            component = "marginal")

>>>>

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
library("tidyverse")
library("easystats")
library("ggplot2") #plots
#library("sjstats") #test statistics
#library("sjPlot")
#library("sjmisc")
##library("insight")
#library("see")
#library("performance")
library("ggraph")
#library("parameters")
library("lme4")
#library("psych") ## correlation matrix
library("table1")
library("ggeffects")
#library("gghighlight")
#library("texreg")
library("kableExtra")
#library("naniar") # missingness
library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
=library("rstan")
library("brms")
library("bayesplot")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
library("WeightIt")# inverse probability weighting. 
library("emmeans")
library("splines")
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
cite_packages(include_R = TRUE)

citation("daggity")
toBibtex(citation("ggdag"))
print(citation("EValue") , bibtex=TRUE)
```

@@

df <- d %>%
  dplyr::mutate(male2 = ifelse(gender != "man", 1 , 2)) %>% # for index categorical variable, not change of meaning for gender. male and people who do not identify as male.
  dplyr::mutate(male = factor(ifelse(gender != "man", "male" , "notmale"))) %>%
  rename(
    rel_CHURCHFREQ   = rel_1,
    # factor need to recode (eg 7 as 0)// yikes factor transformed into a number
    rel_PRAYERFREQ = rel_2,
    # factor need to recode (eg. 7 as 0)// yikes factor transformed into a number
    IS_RELIIGOUS = rel_3,
    # factor 1 = yes, 2 = no, 3 = atheist// yikes factor transformed into a number
    # NOOO revers scorred (1= religious, 2= not religious, 3=atheist) [R] So note that 3 = religious!!
    BELONGS_DENOMINATION = rel_4,
    # relig
    rel_EXTENTBELIEVEGOD = rel_5,
    # do you belong to a religion or religious denomination? 1 = yes, 2 = no (!)
    rel_EXTENTBELIEVEAFTERLIFE = rel_6,
    rel_EXTENTSPIRITUAL  = rel_7,
    rel_IMPORTANCERELIGIOUSLIFE = rel_8,
    # 1 to five
    rel_IMPORTANCEBELIEVEGOD = rel_9,
    # 1 to five
    wb_genLIFEQUALITY = wb_gen_1,
    # not defined # also remove second underscore, which BRMS doesn't like
    wb_genSATHEALTH = wb_gen_2,
    # not defined
    wb_phyPAIN = wb_phys_1,
    wb_physNEEDSMEDICALTREAT =  wb_phys_2,
    wb_physHASENERGY =  wb_phys_3,
    wb_physMOBILITY = wb_phys_4,
    wb_physSLEEP = wb_phys_5,
    wb_physCANDODAILYACTIVITIES  = wb_phys_6,
    wb_physSATCAPACITYWORK  = wb_phys_7,
    wb_psychENJOYLIFE = wb_psych_1,
    wb_psychMEANING  = wb_psych_2,
    wb_psychCONCENTRATE  = wb_psych_3,
    wb_psychLIKESAPPEARANCE  = wb_psych_4,
    wb_psychSATSELF  = wb_psych_5,
    wb_psychANXIETY  = wb_psych_6,
    wb_socSATPERSONALRELATIONSHIPS  = wb_soc_1,
    wb_socSATSUPPORTFRIENDS  = wb_soc_2
    #   wb_socSATSEX   = wb_soc_3,
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = as.factor(IS_RELIIGOUS),
    denomination = as.factor(denomination),
    ethnicity = as.factor(ethnicity),
    country = as.factor(country)
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = recode_factor(
      IS_RELIIGOUS,
      "0" = "atheist",
      "0.5" = "not_religious",
      "1" = "religious"
    )
  )
max(df$rel_EXTENTBELIEVEGOD)
max(df$rel_CHURCHFREQ)
length(unique(df$country))
table(df$country)
```

@@

d1 <- df %>%
  dplyr::filter(
   #  !is.na(wb_psychANXIETY),
   #  !is.na(age),
   #  !is.na(rel_CHURCHFREQ),
   # # !is.na(wb_psychMEANING),
   #  !is.na(male),
   #  !is.na(rel_EXTENTBELIEVEGOD),
  ) %>%
  dplyr::mutate(
    anx = as.integer(6- wb_psychANXIETY), # reverse coded! rescale 1-5
    religious = as.integer(IS_RELIIGOUS), #(1= religious, 2= not religious, 3=atheist) [R]
    #put outcome in ST units (see McElreath 2021)  # not necessary
    #age_s = scale(age),
    ch = rel_CHURCHFREQ,
  #  mn  = wb_psychMEANING,
    edu = education,
    bg =  rel_EXTENTBELIEVEGOD#,
  #  ch_s = scale(rel_CHURCHFREQ),
  #  mn_s = scale(wb_psychMEANING),
   # bg_s = scale(rel_EXTENTBELIEVEGOD)
  ) %>%
  dplyr::select(anx,
                ch,
                age,
                ses,
                #    mn,
                edu,
                bg,
                # anx_s,
                # age_s,
                #  ch_s,
                #  mn_s,
                edu,
                country,
                male,
                religious,
                #   bg_s,
                wb_psychANXIETY)

@@

# 
# ggdag::ggdag(dg2) + theme_dag()
# 
# nocause <- ggdag::ggdag(dg2, text = FALSE, use_labels = "label")  + theme_dag() + labs(title = "Assume unmeasured distressing experience does not affect Belief or Service")
# nocause
# 
# dg0<-ggdag::ggdag_adjustment_set(dg2, node_size = 14, text = FALSE, use_labels = "label") +
#   theme(legend.position = "bottom") +
#   theme_dag() + ggtitle("Adjustment set for religious service
# assuming service does not change from distress")
# 
# dp0
#

dpz <- dagify(
  anx  ~ age + belief + church + male + country + ses,
  belief ~ age + male + country + church + ses + edu,
  church ~ age + male + country + ses +edu,
  ses ~ country  + edu,
  edu ~ country + male + age ,
  U ~ age + ses + country,
  exposure =  "church",
  outcome =   "anx",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
)

ggdag::ggdag(dpz) + theme_dag()
# 
# 
# # graph adjustment sets
dg1<-ggdag::ggdag_adjustment_set(dpz, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for religious belief
assuming belief does not change from distress")

dg1
```

@@

```{r cache = TRUE}
library("naniar")
library(magick)
vis_miss(df) # substantial pattern of missingness in a few variables, 
df
df$wb_soc_3
dff<-df%>%
  select(-wb_soc_3)

miss_graph<- gg_miss_upset(dff)
miss_graphR <-image_ggplot(miss_graph)
# save graph
miss_graph

ggsave(miss_graph,
  path = here::here("figs"),
  width = 16,
  height = 9,
  units = "in",
  filename = "miss_graph.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

@@

  # x is the longitudional dataframe (here 'd_3')
set.seed(1234)
prep <- d1 %>% # Remove what we do not need anymore
    arrange(country) %>%
    dplyr::select(anx,
                  ch,
                  age,
                  edu,
                  bg,
                  edu,
                  country,
                  male,
                  anx, 
                  ses)

table1::table1(~ ch |religious, data = d1)

@@

@@

```{r}
library(mice)
library(tidyverse)
d2<-mice(d1)

#d3<-complete(d2)
#saveRDS(d3,here::here("mods","d3"))
#d3 <-readRDS(here::here("mods","d3"))
d4<-d3%>%
  select(anx, ch, bg, age, edu,male,ses,country,religious)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         religious = factor(religious),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country))

## MICE ONLY RELIGIOUS
table(d1$religious)

# Check
d1r<- d1 %>%
  filter(religious == 3)

hist(d1r$ch)

d2r<-mice(d1r)

#check religious rumbers (1= religious, 2= not religious, 3=atheist) [R] So note that 3 = religious!!

d3r<-complete(d2r)

#saveRDS(d3,here::here("mods","d3r"))
#saveRDS(d3r,here::here("mods","d3r"))

d3 <-readRDS(here::here("mods","d3"))
d3r <-readRDS(here::here("mods","d3r"))

d4<-d3%>%
  select(anx, ch, bg, age, edu,male,ses,country,religious)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country),
         religious = as.factor(religious))

d4r<-d3r%>%
  select(anx, ch, bg, age, edu,male,ses,country)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country))

@@

@@

d1p <- d4 %>% 
  mutate(ipwCH = dch$weights.trunc)

max(d1p$ipwCH)

# weighted for religious only

dchr <- ipw::ipwpoint(
  exposure = ch_s,
  family = "gaussian",
  numerator = ~ 1,
  denominator = ~ age_s + edu_s + male_2 + ses_s + country,
  trunc = 0.01,
  data = as.data.frame(d4r)
)

dr <- d4r %>% 
  mutate(ipwCH = dchr$weights.trunc)

# fine, well below 10
max(dr$ipwCH)

dr$ch_ord <- factor(dr$ch, ordered=TRUE)
table(dr$ch_ord)

levels(dr$ch_ord)<-c("never","rarely","1xpy","holydays","1xpm","1xpw",">1xpw")

levels(dr$ch_ord)
is.ordered(dr$ch_ord)

#saveRDS(dr, here::here("mods","dr"))

# saveRDS(d1p, here::here(
#   "mods","d1p"
# ))

b_orR <- brm(
  anx_s|weights(ipwCH) ~ mo(ch_ord) + (1 + mo(ch_ord) | country),
  data = dr,
   prior = c(
    prior(student_t(3, 0, .5), class = Intercept),
    prior(normal(-.05,.1), class = "b"),
    prior(dirichlet(1,1,1,1,1,1), class = "simo", coef = moch_ord1)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("mods","b_orR")
)

summary(b_orR)

prior_summary(b_orR)

church_plot_R <-plot(ggeffects::ggemmeans(b_or, terms = "ch_ord")) +   xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + labs(title = "Baysian Multi-level Model",
subtitle = "Inverse Probability Weighting") + scale_y_continuous(limits = c(-.5,.5))+ 
  theme_classic()
church_plot_R

### EEMEANS
 b_orR %>% 
  emmeans(~ ch_ord,
          at = list(ch_ord = c("never",">1xpw"),
                    country = NA),
          epred = TRUE) %>% 
  contrast(method = "revpairwise")

effect_draws_b_orR <-  b_orR %>% 
  emmeans(~ ch_ord,
         at = list(ch_ord = c("never",">1xpw"),
                    country = NA),
          epred = TRUE) %>% 
  contrast(method = "revpairwise") %>%
  gather_emmeans_draws()

effect_draws_b_orR %>% mean_hdi()

#SE = (upper limit – lower limit) / 3.92.

# STANDARD ERROR
Roa <- effect_draws_b_orR %>% mean_hdi() 
(Roa$.upper - Roa$.lower)/3.92 #

# SE = .0.06751772

library(EValue)
evalues.OLS(-0.208, se = 0.06751772, sd = 1, delta = 1)
#             point    lower     upper
# RR       0.8275548 0.733842 0.9332348
# E-values 1.7101772       NA 1.3484170
bias_plot(0.9332348, xmax = 6)

average_marginal_effectR <- ggplot(effect_draws_b_orR, aes(x = .value)) +
    stat_halfeye(fill = "dodgerblue") +
  labs(x = "Average marginal effect of church attenance on anxiety", y = "Density",
       subtitle = "Marginal effect (never vs. 1xpw): continuous model") +
  theme_classic() +
       scale_x_continuous(limits=c(-.6,.3)) +
  theme(legend.position = "top")

average_marginal_effectR

grand_mean_ameR <- b_orR %>% 
  emmeans(~ ch_ord,
          at = list(ch_ord = c("never",">1xpw")),
          epred = TRUE, re_formula = NA) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

plot_grand_mean_ameR <- ggplot(grand_mean_ameR, 
                                   aes(x = .value)) +
  stat_halfeye(fill = palette_okabe_ito(order = 5)) +
  labs(x = "Average marginal effect of church attenance on anxiety", y = "Density",
       subtitle = "Marginal effect (never vs. 1xpw): monotonic model") +
  theme_classic() +
    scale_x_continuous(limits=c(-.6,.3)) +
   theme(legend.position = "bottom",
         legend.title = element_text(size = 5),
          legend.text = element_text(size = 2)) 
plot_grand_mean_ameR

grand_mean_autonomy_distR <- b_orR %>% 
  epred_draws(newdata = expand_grid(ch_ord = c("never",
                                               #"rarely","1xpy","holydays","1xpm","1xpw",
                                               ">1xpw")), 
              re_formula = NA)

plot_grand_mean_ordR <- ggplot(grand_mean_autonomy_distR, 
                                   aes(x = .epred, 
                                       fill = ch_ord)) +
  scale_fill_okabe_ito() +
    stat_halfeye(slab_alpha = 0.7) +
    scale_x_continuous(limits=c(-.6,.4)) +
  labs(x = "Predicted anxiety (standardised)", y = "Density",
       fill = "Church frequency",
       subtitle = "Posterior predictions: monotonic model") +
  theme_classic() +
     theme(legend.position = "bottom",
         legend.title = element_text(size = 12),
          legend.text = element_text(size = 8))

plot_grand_mean_ameR + plot_grand_mean_ordR + plot_annotation(tag_levels = "a",  title = "Religious only model")
yola

ggsave(
  plot_grand_mean_ameR,
  path = here::here("figs"),
  width = 12,
  height = 6,
  units = "in",
  filename = "plot_grand_mean_ameR.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

## include religion

```{r}
library(splines)

ipb_ch_ln_no_mediation <- geeglm(
  anx_s ~ ch,
  data = d1p,
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)

## Model misspecification 
ipb_ch_ln_mediation <- geeglm(
  anx_s ~ ch + religious,
  data = d1p,
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)
saveRDS(ipb_ch_ln_mediation, here::here("mods","ipb_ch_ln_mediation"))
saveRDS(ipb_ch_ln_no_mediation, here::here("mods","ipb_ch_ln_no_mediation"))

model_parameters(ipb_ch_ln_mediation)
model_parameters(ipb_ch_ln_no_mediation)

plot(ggeffects::ggemmeans(ipb_ch_ln_mediation, terms = "ch"), add.data = TRUE)

ipb_ch<- geeglm(
  anx_s ~  bs(ch),
  data = d1p,  
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)
saveRDS(ipb_ch, here::here("mods","ipb_ch"))
model_parameters(ipb_ch)

plot(ggeffects::ggemmeans(ipb_ch, terms = "ch[all]"), add.data = TRUE
     )

## Rel only

library(splines)
ipb_ch_lnR<- geeglm(
  anx_s ~ ch,
  data = dr,
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)
#saveRDS(ipb_ch_lnR, here::here("mods","ipb_ch_lnR"))
model_parameters(ipb_ch_lnR)

plot(ggeffects::ggemmeans(ipb_ch_lnR, terms = "ch"), add.data = TRUE
     )

ipb_chR<- geeglm(
  anx_s ~  bs(ch),
  data = dr,  
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)
saveRDS(ipb_chR, here::here("mods","ipb_ch"))
model_parameters(ipb_chR)

plot(ggeffects::ggemmeans(ipb_chR, terms = "ch[all]"), add.data = TRUE
     )

# model_parameters(ipb_bg)

abs(min(d1p$ch_s) - max(d1p$ch_s))
# 3.064032

# sensitivity
evalues.OLS(0.04, se = 0.01, sd = 1, delta = 1.4)

@@

### Religous Only

library(splines)
r_gee <- geeglm(
  anx_s ~ ch, # retain scale
  data = dr,
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)
saveRDS(r_gee, here::here("mods","r_gee"))

hist(dr$ch)

# model_parameters(ipb_bg)

model_parameters(r_gee) # no effect

min(dr$ch_s) + max(dr$ch_s)

# sensitivity
library(EValue)
evalues.OLS(0.2238435, se = 0.01, sd = 1, delta = 1.4)

#bias_plot(0.2238435, xmax = 6)

@@

```{r}
# 
# ipb_bg_noweights <- geeglm(
#   anx_s ~ bg_s + ch_s + age_s + edu_s + male_2 + ses_s,
#   data = d1p,  
#   id = country,
#   corstr = "exchangeable"
# )
# saveRDS(ipb_bg_noweights, here::here("mods","ipb_bg_noweights"))
#

ipb_ch_noweights <- geeglm(
  anx_s ~ bs(ch_s) + age_s + edu_s + male_2 + ses_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable"
)
saveRDS(ipb_ch_noweights, here::here("mods","ipb_ch_noweights"))

msm_lmer <- lmer(
  anx_s ~ bs(ch_s) + age_s + edu_s + male_2 + ses_s +  (1+ ch_s|country),
  data = d1p, 
)
saveRDS(msm_lmer, here::here("mods","msm_lmer"))

msm_lmer_wg <- lmer(
  anx_s ~ bs(ch_s) + (1 + ch_s|country),
  weights = ipwCH,
  data = d1p
)
saveRDS(msm_lmer_wg, here::here("mods","msm_lmer_wg"))

# model_parameters(ipb_bg_noweights)
# model_parameters(ipb_bg_noweights)
# model_parameters(ipb_bg)
# model_parameters(ipb_bg)

model_parameters(ipb_ch_noweights)
model_parameters(ipb_ch)
model_parameters(ipb_ch)
model_parameters(msm_lmer)
model_parameters(msm_lmer_wg)

pred <- ggeffects::ggemmeans(msm_lmer_wg, terms = c("ch_s[all]"))
pred

plot(pred,
    # add.data=T,dot.alpha=.1, 
     facets = F)  + 
  scale_y_continuous(limits=c(-.7,.7)) + 
  theme_classic() + ggtitle("") # title to be suppled

@@

```{r}
listout <- readRDS(here::here("mods","listout"))
modmc <- brm_multiple(
  anx_s ~ ch_s + age_s + edu_s + male_2 +ses_s + (1 + ch_s | country),
  data = listout,
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file=  here::here("mods", "modmc.rds"),
  threads = threading(4)
)

#saveRDS(modmc, here::here("mods", "modmc.rds"))
summary(modmc)

```
## Bayesian wieghted regression

```{r}
listout <- readRDS(here::here("mods","listout"))
modmc_wt_linear <- brm(
  anx_s|weights(ipwCH) ~ ch_s + (1 + ch_s | country),
  data = d1p,
    prior = c(
    prior(normal(0, .1), class = Intercept),
    prior(normal(-.1,.1), class = b)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("mods","modmc_wt_linear")
)
#saveRDS(modmc, here::here("mods", "modmc.rds"))
summary(modmc_wt_linear)

prior_summary(modmc_wt_linear)
summary(modmc_wt_linear)

library(brms)
library(splines)

listout <- readRDS(here::here("mods","listout"))
modmc_wt_priorStrong <- brm(
  anx_s|weights(ipwCH) ~ bs(ch_s) + (1 + ch_s | country),
  data = d1p,
    prior = c(
    prior(student_t(3, 0,.25), class = Intercept),
    prior(normal(-.05, .1), class = b)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("mods","modmc_wt_priorStrong")
)

# prior summary

prior_summary(modmc_wt_priorStrong)
